### 2018-05-30 submission/manuscript.Rmd
fix superscript in intro

**Results.** When analyzing fecal samples we observed that the range in the number of OTUs detected was not consistent between HiFi DNA polymerases at 35 cycles (Accuprime = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_max)` (min - max) versus Phusion = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`). Additionally, the median number of OTUs varied by HiFi DNA polymerase used (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001). When analyzing mock community samples the variation in the number of OTUs detected by the polymerases was observable as early as 20 cycles (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`). There also was a large range in the number of OTUs amplified by the polymerases at 35 cycles (Accuprime = `r filter(mock_num_otu_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_min)` - `r filter(mock_num_otu_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_max)` versus Phusion = `r filter(mock_num_otu_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(mock_num_otu_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`). Chimera prevalence in mock communities varied by polymerase with differences being most notable at 35 cycles (Kappa = `r round((filter(error_summary, cycles == "35x", taq == "K") %>% pull(chimera_prevalence_median))*100, digits = 2)`% (median) versus Platinum = `r round((filter(error_summary, cycles == "35x", taq == "PL") %>% pull(chimera_prevalence_median))*100, digits = 2)`%) and this variation persisted after chimera removal using VSEARCH. We also observed positive correlations between chimera prevalence and the number of OTUs with Platinum having the highest (R^2 = `r max(pull(r2_table, r2))`) and Kappa having the worst (R^2 = `r min(pull(r2_table, r2))`).

>>>>

**Results.** When analyzing fecal samples we observed that the range in the number of OTUs detected was not consistent between HiFi DNA polymerases at 35 cycles (Accuprime = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_max)` (min - max) versus Phusion = `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(fecal_numOTU_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`). Additionally, the median number of OTUs varied by HiFi DNA polymerase used (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001). When analyzing mock community samples the variation in the number of OTUs detected by the polymerases was observable as early as 20 cycles (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`). There also was a large range in the number of OTUs amplified by the polymerases at 35 cycles (Accuprime = `r filter(mock_num_otu_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_min)` - `r filter(mock_num_otu_data, cycles == "35x", taq == "Accuprime") %>% pull(taq_max)` versus Phusion = `r filter(mock_num_otu_data, cycles == "35x", taq == "Phusion") %>% pull(taq_min)` - `r filter(mock_num_otu_data, cycles == "35x", taq == "Phusion") %>% pull(taq_max)`). Chimera prevalence in mock communities varied by polymerase with differences being most notable at 35 cycles (Kappa = `r round((filter(error_summary, cycles == "35x", taq == "K") %>% pull(chimera_prevalence_median))*100, digits = 2)`% (median) versus Platinum = `r round((filter(error_summary, cycles == "35x", taq == "PL") %>% pull(chimera_prevalence_median))*100, digits = 2)`%) and this variation persisted after chimera removal using VSEARCH. We also observed positive correlations between chimera prevalence and the number of OTUs with Platinum having the highest (R^2^ = `r max(pull(r2_table, r2))`) and Kappa having the worst (R^2^ = `r min(pull(r2_table, r2))`).

### 2018-05-30 submission/manuscript.tex
fix superscript in intro

\textbf{Results.} When analyzing fecal samples we observed that the
range in the number of OTUs detected was not consistent between HiFi DNA
polymerases at 35 cycles (Accuprime = 84 - 106 (min - max) versus
Phusion = 84 - 136). Additionally, the median number of OTUs varied by
HiFi DNA polymerase used (P-value \textless{} 0.0001). When analyzing
mock community samples the variation in the number of OTUs detected by
the polymerases was observable as early as 20 cycles (P-value = 0.002).
There also was a large range in the number of OTUs amplified by the
polymerases at 35 cycles (Accuprime = 15 - 20 versus Phusion = 14 - 73).
Chimera prevalence in mock communities varied by polymerase with
differences being most notable at 35 cycles (Kappa = 5.71\% (median)
versus Platinum = 26.62\%) and this variation persisted after chimera
removal using VSEARCH. We also observed positive correlations between
chimera prevalence and the number of OTUs with Platinum having the
highest (R\^{}2 = 0.974) and Kappa having the worst (R\^{}2 = 0.478).

>>>>

\textbf{Results.} When analyzing fecal samples we observed that the
range in the number of OTUs detected was not consistent between HiFi DNA
polymerases at 35 cycles (Accuprime = 84 - 106 (min - max) versus
Phusion = 84 - 136). Additionally, the median number of OTUs varied by
HiFi DNA polymerase used (P-value \textless{} 0.0001). When analyzing
mock community samples the variation in the number of OTUs detected by
the polymerases was observable as early as 20 cycles (P-value = 0.002).
There also was a large range in the number of OTUs amplified by the
polymerases at 35 cycles (Accuprime = 15 - 20 versus Phusion = 14 - 73).
Chimera prevalence in mock communities varied by polymerase with
differences being most notable at 35 cycles (Kappa = 5.71\% (median)
versus Platinum = 26.62\%) and this variation persisted after chimera
removal using VSEARCH. We also observed positive correlations between
chimera prevalence and the number of OTUs with Platinum having the
highest (R\textsuperscript{2} = 0.974) and Kappa having the worst
(R\textsuperscript{2} = 0.478).
